---
title: "Informe Economía Estadounidense"
author: "Subgerencia de Estudios Económicos"
crossref:
  fig-title: Gráfico     # (default is "Figure")
  tbl-title: Tabla     # (default is "Table")
  fig-prefix: Gráfico   # (default is "Figure")
  tbl-prefix: Tabla    # (default is "Table")
format:
  html:
    toc: true
    code-fold: false
  pdf: 
    documentclass: report
    classoption: landscape
    geometry:
      - top=5mm
      - left=10mm
      - right=10mm
editor: visual
---

```{r setup, include=FALSE}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(plotly)
library(purrr)
library(fredr)
fredr_set_key("672bd1f2e0dc506a82c3c6195d0d0214")
observation_start = as.Date("2015-01-01")
observation_end = as.Date("2023-12-01")
```

## Real GDP

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "GDPC1",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      'PIB de USA, Valores Constantes',
      '<br>','<sup>',
      'Miles de Millones de USD',
      '</sup>')))
```

## Unemployment Rate

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "UNRATE",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      'Tasa de Desempleo de USA',
      '<br>','<sup>',
      'Porcentaje',
      '</sup>')))
```

## Core Inflation

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "CPILFESL",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      'IPC Subyacente de USA (Excluye Alimentos y Energía)',
      '<br>','<sup>',
      'Índice',
      '</sup>')))
```

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "CPIAUCSL",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      'IPC Total de USA (Excluye Alimentos y Energía)',
      '<br>','<sup>',
      'Índice',
      '</sup>')))
```

## GDP Growth

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "A191RL1Q225SBEA",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      'PIB de USA',
      '<br>','<sup>',
      'Tasa de crecimiento, trimestral anualizada',
      '</sup>')))
```

## Manufacturing Index

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "IPB50001N",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      'Manufacturing Index',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Real Personal Income

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "RPI",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      'Real Personal Income',
      '<br>','<sup>',
      'Tasa de crecimiento, trimestral anualizada',
      '</sup>')))
```

## Real Personal Consumption

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "PCEC96",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      'Real Personal Consumption Expenditures',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Business Investment in Nonresidential Structures

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "B009RX1Q020SBEA",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Federal Government Spending: Defense

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "A824RX1Q020SBEA",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Federal Government Spending: Nondefense

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "A825RX1Q020SBEA",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## State and Local Government Spending

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "SLCEC1",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Core CPI Inflation

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "CPILFESL",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      'Índice IPC Subyacente',
      '</sup>')))
```

## CPI: Services

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "CUSR0000SAS",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## CPI: Food

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "CPIUFDNS",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Payroll Employment

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "CES0500000017",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Average Hourly Earnings

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "CEU0500000003",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Employment Cost Index

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "CIU2010000000510I",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Exports of Goods and Services

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "EXPGSC1",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Imports of Goods and Services

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "IMPGSC1",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Crude Oil Prices (WTI)

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "MCOILWTICO",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## Fed Funds Effective Rate

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "FEDFUNDS",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## CBOE Volatility Index

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "VIXCLS",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```

## S&P 500

```{r, comment="", warning=F, message=F, echo=F}
fredr(series_id = "SP500",
  observation_start = observation_start,
  observation_end = observation_end) %>%
  plot_ly(., x = ~date, y = ~value, 
          type = 'scatter', mode = 'lines') %>% 
  layout(
    xaxis = list(title = ""),
    yaxis = list (title = ""),
    title = list(
      text = paste0(
      '',
      '<br>','<sup>',
      '',
      '</sup>')))
```
